Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-16 cover_letter.tex
Addressed remarks concerning curiosity + generation of refering expressions and added relevant papers

@@

\subsection{``the authors are kindly referred to the work by Zender et al.
(2009, IJCAI) on reference resolution in OWL-DL ontology knowledge bases using
SPARQL queries''}

A reference to Zender's work has been added to the \emph{Related work} section.

@@

\subsection{``the authors are kindly referred to work on the Generation and
Resolution of Referring Expressions (GRE, RRE) from the Computational
Linguistics and Natural Language Processing community, e.g. Dale\&Reiter,
Krahmer\&Theune, Kelleher ''}

>>>>

A mention to the Dora robot has been added in section 2.1.

@@

\subsection{``Mention work on Generation and Resolution of Referring Expressions''}

Thanks for pointing out the work that has been done in this research community.
Even if our contribution focuses more on the grounding of concepts from 
multi-modal knowledge source, these contribution are of definitive 
interest for us.

A reference to Zender's work has been added to the \emph{Related work} 
section, along with a reference to Dale and Reiter paper from 1995.

@@

### 2011-07-16 paper_knowledge.tex
Addressed remarks concerning curiosity + generation of refering expressions and added relevant papers

Zender et al.~\cite{Zender2009} address the generation of referring expressions
(\emph{GRE}) in situated dialogue for topological knowledge.  They consider
both the reference resolution and reference description tasks, and rely on
OWL-DL representation and SPARQL\footnote{{\em SPARQL Protocol and RDF Query
Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} to extract
\emph{topological contexts} from their knowledge base.

@@

This list does not cover all the possible features that could be exposed by a
symbolic knowledge management system. Bio-inspired memory management (the
ability to forget or reinforce knowledge) or curiosity (the ability to
identify lacking knowledge and actively trigger behaviors to acquire
it\fixme{cite Howa}), to give some examples, could arguably be added to the
list. However, this first analysis sets a convenient reference frame to
understand and evaluate knowledge representation systems, including the
\textsc{ORO} knowledge management system we propose.

>>>>

Zender et al.~\cite{Zender2009} address the generation of referring expressions
(\emph{GRE},~\cite{Dale1995}) in situated dialogue for topological knowledge.  They consider
both the reference resolution and reference description tasks, and rely on
OWL-DL representation and SPARQL\footnote{{\em SPARQL Protocol and RDF Query
Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} to extract
\emph{topological contexts} from their knowledge base.

@@

This list does not cover all the possible features that could be exposed by a
symbolic knowledge management system. Bio-inspired memory management (the
ability to forget or reinforce knowledge) or curiosity (the ability to identify
lacking knowledge and actively trigger behaviours to acquire it -- Hawes et
al.~\cite{Hawes2011} have contributions in this field, with their \emph{Dora}
robot which is endowed with motivation mechanisms to explore unknown parts of
the environment), to give some examples, could arguably be added to the list.
However, this first analysis sets a convenient reference frame to understand
and evaluate knowledge representation systems, including the \textsc{ORO}
knowledge management system we propose.
